render_annotations

### 2022-01-06 paper/manuscript/initial_submission/appendix.Rmd
rename writing folder structure

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)

knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

@@

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))

@@

# function to return prfs
 return_prf_short <- function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

@@

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old. Each dot represents the average position from one video within a given age range.", warning=F}

@@

# Detection threshold estimations

```{r}
# with all thresholds
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r}
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

 return_tpr = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  tn=sum(eval == "TN")
  tpr = tp / (tp + fn)
  return(tpr)
 }

return_fpr = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  tn=sum(eval == "TN")
  fpr = fp / (fp + tn)
  return(fpr)
 }

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
```

```{r}
face_roc = ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate') +
  ggtitle('Face detections') +
  theme(legend.position = 'none')

hand_roc = ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate') +
  ggtitle('Hand detections') +
  theme(legend.position = 'none')

```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.cap="ROC curves relating the rate of true vs. false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
ggarrange(face_roc, hand_roc, nrow=1)
```

# OpenPose Error Analyses
```{r}
# remove big data frame with thresholds
rm(all_gold_sample_frames_op)

# without thresholds
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections.RData"))

    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
```

```{r}
# add age day bins to gold_sample
load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

gold_sample <- gold_sample %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```

```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  num_detect = length(eval)
  out <- data.frame(p,r,f,num_detect)
  return(out)
 }

```{r}
prf_by_age_faces <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$face_eval_ketan))

prf_by_age_hands <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$hand_eval_ketan)) 
```

```{r}
# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.

# return_prf_short(gold_sample$hand_eval_ketan_center)
# return_prf_short(gold_sample$face_eval_ketan_center)
```

```{r det_perf_by_age, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}

prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)

prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')
```

```{r}
ggarrange(p1, p2, nrow=1)
```

```{r}
# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Precision - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# 
# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Recall - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# #
# ggarrange(p1,p2,p3)

```{r}
load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta

num_videos_annotated = sum(!is.na(meta$Location))
videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
```

```{r}
gold_sample_by_location <- gold_sample %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
```

```{r}
prf_by_location_faces <-  gold_sample_by_location %>%
  group_by(Location) %>%
  do(return_prf(.$face_eval_ketan)) %>%
  filter(num_detect > 50)

prf_by_location_hands <-  gold_sample_by_location %>%
  group_by(Location) %>%
  do(return_prf(.$hand_eval_ketan)) %>%
  filter(num_detect > 50)
```

```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location. Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score') + ggtitle("Face detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score') + ggtitle("Hand detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

ggarrange(p1, p2, nrow=1)
```

# OpenPose Annotation Examples
```{r include=FALSE}
load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))

fp_face_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FP')

fp_hand_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(hand_eval_ketan == 'FP')

fn_face_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FN')

fn_hand_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FN')

images_to_render =  fp_hand_examples
which_images = 'fp_hand_examples'

public_urls = unique(images_to_render$public_url)
img_names_short = unique(images_to_render$img_name)

dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
  }

```{r}
det_types = c('FP','FN')

render_examples = FALSE
if (render_examples == TRUE) {
for (det_type in det_types) {
  to_render_hands <- d %>%
    distinct(vid_name, frame, public_url) %>%
    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
    filter(hand_eval_ketan == det_type) %>%
    ungroup() %>%
    dplyr::sample_n(7)

  image_read(to_render_hands$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))

  ###
    to_render_faces <- d %>%
    distinct(vid_name, frame, public_url) %>%
    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
    filter(face_eval_ketan == det_type) %>%
    ungroup() %>%
    dplyr::sample_n(7)

  image_read(to_render_faces$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))

}
}

```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
error_examples <- png::readPNG("figs/OP_errors.png")
grid::grid.raster(error_examples)
```

## Location of OpenPose False Positives

Below we visualize the locations of the 1229 faces (in 1093 frames) that OpenPose detected in the gold set frames that were not actually there, as well as the 1778 OpenPose false positive hands (in 1237 frames) from the gold set.
The average location of OpenPose's false positives for both faces (left) and hands (right) are somewhat more common in the center of the frame, but some are scattered across the frame.
Qualitatively, the location of these false positives do not look much different than the true positive detections.

```{r density-op-fps, fig.width=6, fig.height=3}
load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  +
  scale_y_reverse()

ggpubr::ggarrange(p1, p2)
```

# Activity by Location

```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
  select(Child, `File Name`, Activity, Location) %>%
  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
  pivot_longer(cols = starts_with("Act."), 
                                        names_to = "activity_index",
                                        names_prefix = "Act.",
                                        values_to = "Activity",
                                        values_drop_na = T) %>%
  mutate(Activity = case_when(Activity=="Waving" ~ "Gesturing",
                              Activity=="Imitation" ~ "Imitating",
                              Activity=="Talking Walk" ~ "Walking",
                              Activity=="Tidying" ~ "Cleaning",
                              Activity=="Preparing for Outing" ~ "Getting Changed/Dressed",
                              Activity=="Play Pretend" ~ "Playing",
                              TRUE ~ Activity))

# include videos with multiple locations
meta_long <- meta_wide %>% 
  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',') %>%
  pivot_longer(cols = starts_with("Loc."),
               names_to = "location_index",
               names_prefix = "Loc.",
               values_to = "Location",
               values_drop_na = T)

single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")

# single-location videos
meta_long_1loc <- meta_wide %>%
  filter(is.element(Location, single_locations)) %>%
  filter(Activity!="N/A", Activity!="Consequence", Activity!="Gesturing")

# what is "California Room" ?
meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))

loc_freq = sort(table(meta_long_1loc$Location))

# multi-location videos
meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
                     Activity!="Gesturing", Activity!="Look and Listen", 
                     Location!="N/A", Location!="California Room",
                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
# single location videos
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
```

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Motor Milestones Analysis Details

We examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.

We tried including random slopes by age and milestone, but the models did not converge and/or were singular. Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).

```{r, get-milestones, echo=F}
motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
# A and S are sitting at 6mos
face_hand_by_age_milestones <- face_hand_by_age %>%
  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
                      (child_id=="A" & age_day_bin >= 10) | 
                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
                       (child_id=="A" & age_day_bin > 13) |
                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
  mutate(age = age_day_bin)

library(lmerTest)
# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
# so we drop random slopes

face_all <- lmer(prop_faces ~ age * (sit + cruise + walk) + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(face_all) # cruise+ age:cruise-

hand_all <- lmer(prop_hands ~ age * (sit + cruise + walk) + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(hand_all) # cruise+ age:cruise-.

face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
# make models compatible with stargazer
class(face_sit) <- "lmerMod"
class(hand_sit) <- "lmerMod"
class(face_cruise) <- "lmerMod"
class(hand_cruise) <- "lmerMod"
class(face_walk) <- "lmerMod"
class(hand_walk) <- "lmerMod"
```

## Sitting

Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.

```{r, include=F, results='asis'}
#summary(face_sit) # ns
stargazer(face_sit, title="Predicting Faces by Ability to Sit", 
          header=F, dep.var.labels = "Proportion of Faces")

stargazer(face_sit, hand_sit)
```

```{r, include=F, results='asis'}
#summary(hand_sit) # ns
stargazer(hand_sit, title="Predicting Hands by Ability to Sit", 
          header=F, dep.var.labels = "Proportion of Hands")
```

```{r, results='asis'}
stargazer(face_sit, hand_sit, title="Change in Face and Hand Prevalence by Ability to Sit", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

## Cruising

As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).

```{r, include=F, results='asis'}
#summary(face_cruise) 
# age+., cruise+*, age*cruise-*
stargazer(face_cruise, title="Predicting Faces by Ability to Cruise", 
          header=F, dep.var.labels = "Proportion of Faces")
```

```{r, include=F}
f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces") + theme_classic()

h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands") + theme_classic()

ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
```

```{r, include=F, results='asis'}
#summary(hand_cruise) 
# cruise+*, age*cruise-.
stargazer(hand_cruise, title="Predicting Hands by Ability to Cruise", 
          header=F, dep.var.labels = "Proportion of Hands") 
```

```{r, results='asis'}
stargazer(face_cruise, hand_cruise, title="Change in Face and Hand Prevalence by Ability to Cruise", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

## Walking

As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).

```{r, include=F, results='asis'}
#summary(face_walk) # ns
stargazer(face_walk, title="Predicting Faces by Ability to Walk", 
          header=F, dep.var.labels = "Proportion of Faces")
```

```{r, include=F, results='asis'}
#summary(hand_walk) # walk+.
stargazer(hand_walk, title="Predicting Hands by Ability to Walk", 
          header=F, dep.var.labels = "Proportion of Hands")
```

```{r, results='asis'}
stargazer(face_walk, hand_walk, title="Change in Face and Hand Prevalence by Ability to Walk", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
```

@@

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

@@

#

@@

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old. Each dot represents the average position from one video within a given age range."}

@@

### 2022-01-06 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
rename writing folder structure

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

@@

```{r}
# Read in data 
## Face/hand detections by video
load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
```

```{r}
# load bounding box summaries by video
load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
```

```{r}
# gold sample annotations for these specific frames
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r}
# load high confidence detections for gold sample frames
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData'))
all_gold_sample_frames_op_hc = all_gold_sample_frames_op
```

```{r}
# load all detections for gold sample frames
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
```

@@

```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

@@

### Restricting detections to the center field-of-view
Given that the fish-eye lens may have distorted the edges of the visual field in the videos, we also examined whether we would see improved precision by restricting the included detections to the center field-of-view, and excluding detections that occured in the outer 20\% of each frame. This restricted field-of-view is also more comparable to video data from other head-mounted cameras. However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall. Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`. For hands, the F-score for center detections was `r round(hand_performance)center[3],2)`, with a precision of `r round((hand_performance)[1],2)` and recall of `r round((hand_performance)[2],2)`. Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands. Appendix Figure \ref{fig: density-op-fps} illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.

@@

## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%c
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].

@@

## Variability in social information across learning contexts 
```{r}
load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta

@@

Of course, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data. While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in infant egocentric videos -- as in @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.   While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not perform accurately enough to answer certain fine-grained research questions. Going forward, we suggest that researchers continue to compare a small set of manual annotations relevant to their research questions of interest to OpenPose's performance.

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

```{r}
# Read in data 
## Face/hand detections by video
load(file=here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections
```

```{r}
# load bounding box summaries by video
load(file=here::here('data/preprocessed_data_2022/bounding_box_summaries_all.RData'))
```

```{r}
# gold sample annotations for these specific frames
load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r}
# load high confidence detections for gold sample frames
load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_high_conf_detections.RData'))
all_gold_sample_frames_op_hc = all_gold_sample_frames_op
```

```{r}
# load all detections for gold sample frames
load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
```

@@

```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2022/child_adult_hand_annotations_by_frame.RData'))
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

@@

### Restricting detections to the center field-of-view
Given that the fish-eye lens may have distorted the edges of the visual field in the videos, we also examined whether we would see improved precision by restricting the included detections to the center field-of-view, and excluding detections that occured in the outer 20\% of each frame. This restricted field-of-view is also more comparable to video data from other head-mounted cameras. However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall. Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`. For hands, the F-score for center detections was `r round(hand_performance_center[3],2)`, with a precision of `r round(hand_performance_center[1],2)` and recall of `r round(hand_performance_center[2],2)`. Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands. Appendix Figure \ref{fig: density-op-fps} illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.

@@

## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].

@@

## Variability in social information across learning contexts 
```{r}
load(here::here('data/preprocessed_data_2022/saycam_metadata.RData')) # meta

@@

Of course, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data. While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in infant egocentric videos -- as in @long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.   While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not perform accurately enough to answer certain fine-grained research questions. Going forward, we suggest that researchers continue to compare a small set of manual annotations relevant to their research questions of interest to OpenPose's performance.
